---
title: "H-1B Visa"
author: "Cheng Zeng, Wenyu Zeng, Chao Zhou, Spencer Stucky"
date: "10/14/2019"
output:
  html_document:
    toc: yes
    toc_depth: 4
    fig.align: "center"
    toc_float: yes
    theme: readable
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r, include = F}
library(dplyr)
h1b <- read.csv('h1b_datahubexport_2009-2019.csv')
```
How have U.S. H1b visa acceptances and denials changed over the course of 2015-2019?1a) How does industry effect H1b visas from the time spanning 2015-2019?

# Chapter 1: Introduction

H-1B visa is a type of non-immigrate visa of United States that under the Immigration and Nationality Act since 1952. This visa allows foreign workers (individual) to enter United Stated to temporarily be employed by U.S. employers in specialty occupations. (Path2usa) With the development of the world, more and more people are looking for opportunities in U.S. Therefore, the number of applications for H-1B are rising every year. Each year, the total number of H-1B petitions that U.S. congress allowed to approve for a fiscal year is 65,000 for regular cap and 20,000 master’s exemption. (USCIS) According to the summary of USCIS H-1B 2019, there are more than 190,000 applications were submitted and 94,213 for regular quota and 95,885 for master quota. (USCIS) However, after Donald Trump become president, he signed the "Buy American, Hire American" executive order in April 2017. (USCIS) Though, this order helps U.S. employers hire most-skills foreign employees, the approval of this visa became harder and harder.

Nonetheless, politics is not the only factor that affects H-1B’s approval rate, but industries and location are also impact it. In this report, we will focus on the relationship in ______________________________________________.

# Chapter 2: Description of Data
xxxxxxx
```{r, echo=FALSE}
str(h1b)
```
xxxxxxx

# Chapter 3: Industries Factor

## 3.1: Industries vs NAICS 
### 3.1.1: Initial Application

```{r initial, echo=FALSE} 
library(ggplot2)
h1b$naics = as.factor(h1b$NAICS)
# use group by to combine same industry together to calculate the total initial application amount.
initial <- h1b %>% group_by(naics) %>% summarize( totaliniaccpt = sum(Initial.Approvals, na.rm = T), #shows total number of initail approvals
                                                  totaliniden = sum(Initial.Denials, na.rm = T), # shows total number of initial denials
                                                  totalinitial = sum(Initial.Approvals,na.rm = T)+sum(Initial.Denials,na.rm = T), # shows total number of initial application
                                                  iaccptperc = (totaliniaccpt/totalinitial)*100, round(iaccptperc, digits = 2), # percentage of initial approval rate
                                                  idenperc = (totaliniden/totalinitial)*100, round(idenperc, digits = 2)) #percentage of initial denial rate

ggplot(initial, aes(x = naics, y = iaccptperc, color = naics, fill = naics)) + # percentage of initial approvals rate and color by industry code
  geom_bar(stat ="identity") + 
  xlab("NAICS CODE") + 
  ylab("Total Initial Approvals Percentage")
ggplot(initial, aes(x = naics, y = idenperc, color = naics, , fill = naics)) + # percentage of initial denials rate and color by industry code
  geom_bar(stat ="identity") + 
  xlab("NAICS CODE") + 
  ylab("Total Initial Denials Percentage")

```
XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
XXXXXXXXXXXXXXXXXXXXXXX
XXXXXXXXXXXXXXXXX
XXXXXXXXXXXXXX
XXXXXXXXXX
XXXXXXXXX
XXXX
XXX
X
X
### 3.1.2: Continuing Application
```{r continuing, echo=FALSE}
# use group by to combine same industry together to calculate the total continuing application amount.
continuing <- h1b %>% group_by(naics) %>% summarize( totalconaccpt = sum(Continuing.Approvals, na.rm = T),
                                                  totalconden = sum(Continuing.Denials, na.rm = T),
                                                  totalcontinue = sum(Continuing.Approvals,na.rm = T)+sum(Continuing.Denials,na.rm = T),
                                                  caccptperc = (totalconaccpt/totalcontinue) * 100,
                                                  cdenperc = ( totalconden /totalcontinue) * 100 )
ggplot(continuing, aes(x = naics, y = caccptperc, color = naics, fill = naics)) + geom_bar(stat ="identity") + xlab("NAICS CODE") + ylab("Total Continuing Approvals Percentage")
ggplot(continuing, aes(x = naics, y = cdenperc, color = naics, fill = naics)) + geom_bar(stat ="identity") + xlab("NAICS CODE") + ylab("Total Continuing Denials Percentage")
```


## 3.2: Industries vs NAICS by Year

### 3.2.1: Initial Application

```{r fig.width=12, fig.height=9,initialwithyear, echo=F}
#install.packages("directlabels")
library(directlabels)

initialbyyear <- h1b %>% group_by(Fiscal.Year, naics) %>% summarize( totaliniaccpt = sum(Initial.Approvals, na.rm = T),
                                                  totaliniden = sum(Initial.Denials, na.rm = T),
                                                  totalinitial = sum(Initial.Approvals,na.rm = T)+sum(Initial.Denials,na.rm = T),
                                                  iaccptperc = (totaliniaccpt/totalinitial)*100, 
                                                  idenperc = (totaliniden/totalinitial)*100)

ggplot(initialbyyear, aes(x=Fiscal.Year, y=iaccptperc)) + 
    geom_line(aes(color=naics, group=naics), size = 1) +   # create the line by nacis code
    ggtitle("Line Plot of Industry and  Initial Approvals Percentage by Year")+
    geom_point(aes(color=naics), size=3) +  # for visualization purpose, we set up the point for each year so people can directly see the rate change of industry by year 
    theme(plot.title = element_text(hjust = 0.5)) +  # since we change the size of the figer, we need to relocate the fig name to center
    xlab("Year")+ ylab("Percentage(%)")+  # rename x and y axis names
    geom_dl(aes(label = naics, color = naics), method = list(dl.combine("first.polygons", "last.polygons"), cex = 1))+  #set up label for each line
    scale_x_continuous(breaks=seq(2009, 2019, 1))+   # changing the scale for both x and y axis
    scale_y_continuous(breaks=seq(50, 100, 5)) 

ggsave("iaccptperc.png", width=12, height=9)

ggplot(initialbyyear, aes(x=Fiscal.Year, y=idenperc)) + 
    geom_line(aes(color=naics, group=naics), size = 1) + 
    ggtitle("Line Plot of Industry and  Initial Denials Percentage by Year")+
    geom_point(aes(color=naics), size=3) +
    theme(plot.title = element_text(hjust = 0.5)) + 
    xlab("Year")+ ylab("Percentage(%)")+
    geom_dl(aes(label = naics, color = naics), method = list(dl.combine("first.polygons", "last.polygons"), cex = 1))+
    scale_x_continuous(breaks=seq(2009, 2019, 1))+
    scale_y_continuous(breaks=seq(50, 100, 5))
ggsave("idenperc.png", width=12, height=9)


```


### 3.2.2: Continuing Application

```{r fig.width=12, fig.height=9, continuewithyear, echo = 0}
# use group by to combine same industry together to calculate the total continuing application amount.
continuingbyyear <- h1b %>% group_by(Fiscal.Year, naics) %>% summarize( totalconaccpt = sum(Continuing.Approvals, na.rm = T),
                                                  totalconden = sum(Continuing.Denials, na.rm = T),
                                                  totalcontinue = sum(Continuing.Approvals,na.rm = T)+sum(Continuing.Denials,na.rm = T),
                                                  caccptperc = (totalconaccpt/totalcontinue) * 100,
                                                  cdenperc = ( totalconden /totalcontinue) * 100 )


ggplot(continuingbyyear, aes(x=Fiscal.Year, y=caccptperc)) + 
    geom_line(aes(color=naics, group=naics), size = 1) + 
    ggtitle("Line Plot of Industry and Continuing Approvals Percentage by Year")+
    geom_point(aes(color=naics), size=3) +
    theme(plot.title = element_text(hjust = 0.5)) + 
    xlab("Year")+ ylab("Percentage(%)")+
    geom_dl(aes(label = naics, color = naics), method = list(dl.combine("first.polygons", "last.polygons"), cex = 1))+
    scale_x_continuous(breaks=seq(2009, 2019, 1))+
    scale_y_continuous(breaks=seq(50, 100, 5))

ggsave("caccptperc.png", width=12, height=9)

ggplot(continuingbyyear, aes(x=Fiscal.Year, y=cdenperc)) + 
    geom_line(aes(color=naics, group=naics),size = 1) + 
    ggtitle("Line Plot of Industry and Continuing Denials Percentage by Year")+
    geom_point(aes(color=naics), size=3) +
    theme(plot.title = element_text(hjust = 0.5)) + 
    xlab("Year")+ ylab("Percentage(%)")+
    geom_dl(aes(label = naics, color = naics), method = list(dl.combine("first.polygons", "last.polygons"), cex = 1))+
    scale_x_continuous(breaks=seq(2009, 2019, 1))+
    scale_y_continuous(breaks=seq(50, 100, 5))

ggsave("cdenperc.png", width=12, height=9)

```


```{r}
#install.packages("plotly")
library(plotly)
plot_ly(initialbyyear, x = ~iaccptperc, y = ~Fiscal.Year, z = ~naics, type = 'scatter3d', mode = 'lines', color = ~naics) %>%
  add_markers() %>%
  layout(scene = list(xaxis = list(title = '%'),
                     yaxis = list(title = 'YEAR'),
                     zaxis = list(title = 'naics')))



# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
#chart_link = api_create(p, filename="scatter3d-basic")
#chart_link
```

### 3.2.2: Continuing Application

# Citation

What is H1B Visa? (n.d.). Retrieved October 14, 2019, from https://www.path2usa.com/what-is-h1b-visa.

USCIS Reaches FY 2019 H-1B Cap. (2018, April 6). Retrieved October 14, 2019, from https://www.uscis.gov/news/alerts/uscis-reaches-fy-2019-h-1b-cap.

Buy American and Hire American. (2019, April 26). Retrieved October 14, 2019, from https://www.uscis.gov/legal-resources/buy-american-hire-american-putting-american-workers-first.

Search NAICS Codes by Industry. (n.d.). Retrieved October 15, 2019, from https://www.naics.com/search-naics-codes-by-industry/.


