---
title: "H-1B Visa"
author: "Spencer Stucky, Cheng Zeng, Wenyu Zeng, Chao Zhou"
date: "10/14/2019"
output:
  html_document:
    toc: yes
    toc_depth: 4
    fig.align: "center"
    toc_float: yes
    theme: readable
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r, include = F}
library(dplyr)
library(maps)
h1b <- read.csv('h1b_datahubexport_2009-2019.csv')
#h1b <- h1b[h1b$State %in%state.abb,]
```
How have U.S. H1b visa acceptances and denials changed over the course of 2015-2019?1a) How does industry effect H1b visas from the time spanning 2015-2019?

# Chapter 1: Introduction

H-1B visa is a type of non-immigrate visa of United States that under the Immigration and Nationality Act since 1952. This visa allows foreign workers (individual) to enter United Stated to temporarily be employed by U.S. employers in specialty occupations. (Path2usa) With the development of the world, more and more people are looking for opportunities in U.S. Therefore, the number of applications for H-1B are rising every year. Each year, the total number of H-1B petitions that U.S. congress allowed to approve for a fiscal year is 65,000 for regular cap and 20,000 master’s exemption. (USCIS) According to the summary of USCIS H-1B 2019, there are more than 190,000 applications were submitted and 94,213 for regular quota and 95,885 for master quota. (USCIS) However, after Donald Trump become president, he signed the "Buy American, Hire American" executive order in April 2017. (USCIS) Though, this order helps U.S. employers hire most-skills foreign employees, the approval of this visa became harder and harder.

Nonetheless, politics is not the only factor that affects H-1B’s approval rate, but industries and location are also impact it. In this report, we will focus on the relationship in ______________________________________________.

# Chapter 2: Description of Data
xxxxxxx
```{r, echo=FALSE}
str(h1b)
```
xxxxxxx

# Chapter 3: Industries Factor

## 3.1: Industries vs NAICS 
### 3.1: S.M.A.R.T Question
**How does industry affect H1b visas from the time spanning 2009-2019?**
### 3.2.1: Initial Application

```{r initial, echo=FALSE} 
library(ggplot2)
h1b$naics = as.factor(h1b$NAICS)
# use group by to combine same industry together to calculate the total initial application amount.
initial <- h1b %>% group_by(naics) %>% summarize( totaliniaccpt = sum(Initial.Approvals, na.rm = T), #shows total number of initail approvals
                                                  totaliniden = sum(Initial.Denials, na.rm = T), # shows total number of initial denials
                                                  totalinitial = sum(Initial.Approvals,na.rm = T)+sum(Initial.Denials,na.rm = T), # shows total number of initial application
                                                  iaccptperc = (totaliniaccpt/totalinitial)*100, # percentage of initial approval rate
                                                  idenperc = (totaliniden/totalinitial)*100) #percentage of initial denial rate
# 
# ggplot(initial, aes(x = naics, y = iaccptperc, color = naics, fill = naics)) + # percentage of initial approvals rate and color by industry code
#   geom_bar(stat ="identity") +
#   xlab("NAICS CODE") +
#   ylab("Total Initial Approvals Percentage")
# 
# ggsave("Total Initial Approvals Percentage.png", width=12, height=9)

head(initial,n=5)

ggplot(initial, aes(x = naics, y = idenperc, color = naics, , fill = naics)) + # percentage of initial denials rate and color by industry code
  geom_bar(stat ="identity") + 
  xlab("NAICS CODE") + 
  ylab("Total Initial Denials Percentage") 
ggsave("Total Denial Approvals Percentage.png", width=12, height=9)


```

21(Mining): highest approval rate and lowest denial rate. 
https://www.thermofisher.com/blog/mining/mining-industry-employees-are-in-demand/

72(Accommodation and Food Services): lowest approval rate and highest denial rate

https://www.h1b.biz/hospitality-and-immigration-law-visas-for-chefs-cooks-and-other.html

### 3.2.2: Continuing Application
```{r continuing, echo=FALSE}
# use group by to combine same industry together to calculate the total continuing application amount.
continuing <- h1b %>% group_by(naics) %>% summarize( totalconaccpt = sum(Continuing.Approvals, na.rm = T),
                                                  totalconden = sum(Continuing.Denials, na.rm = T),
                                                  totalcontinue = sum(Continuing.Approvals,na.rm = T)+sum(Continuing.Denials,na.rm = T),
                                                  caccptperc = (totalconaccpt/totalcontinue) * 100,
                                                  cdenperc = ( totalconden /totalcontinue) * 100 )
# ggplot(continuing, aes(x = naics, y = caccptperc, color = naics, fill = naics)) + geom_bar(stat ="identity") + xlab("NAICS CODE") + ylab("Total Continuing Approvals Percentage")
# ggsave("Total Continuing Approvals Percentage.png", width=12, height=9)
head(continuing,n=5)
ggplot(continuing, aes(x = naics, y = cdenperc, color = naics, fill = naics)) + geom_bar(stat ="identity") + xlab("NAICS CODE") + ylab("Total Continuing Denials Percentage")
ggsave("Total Continuing DenialsPercentage.png", width=12, height=9)
```
99: This major group includes establishments which cannot be classified in any other industry. Establishments which can be classified in a division should be classified in the most appropriate industry within that division.
99(Nonclassifiable Establishments): lowest appoval rate and highest denial rate
55(Management of Companies and Enterprises): highest approval rate and lowest denial rate. Financial & Banking.

## 3.3: Industries vs NAICS by Year

### 3.3.1: Initial Application

```{r fig.width=12, fig.height=9,initialwithyear, echo=F}
#install.packages("directlabels")
library(directlabels)

initialbyyear <- h1b %>% group_by(Fiscal.Year, naics) %>% summarize( totaliniaccpt = sum(Initial.Approvals, na.rm = T),
                                                  totaliniden = sum(Initial.Denials, na.rm = T),
                                                  totalinitial = sum(Initial.Approvals,na.rm = T)+sum(Initial.Denials,na.rm = T),
                                                  iaccptperc = (totaliniaccpt/totalinitial)*100, 
                                                  idenperc = (totaliniden/totalinitial)*100)

head(initialbyyear,n=5)
ggplot(initialbyyear, aes(x=Fiscal.Year, y=iaccptperc)) + 
    geom_line(aes(color=naics, group=naics), size = 1) +   # create the line by nacis code
    ggtitle("Line Plot of Industry and  Initial Approvals Percentage by Year")+
    geom_point(aes(color=naics), size=3) +  # for visualization purpose, we set up the point for each year so people can directly see the rate change of industry by year 
    theme(plot.title = element_text(hjust = 0.5)) +  # since we change the size of the figer, we need to relocate the fig name to center
    xlab("Year")+ ylab("Percentage(%)")+  # rename x and y axis names
    geom_dl(aes(label = naics, color = naics), method = list(dl.combine("first.polygons", "last.polygons"), cex = 1))+  #set up label for each line
    scale_x_continuous(breaks=seq(2009, 2019, 1))+   # changing the scale for both x and y axis
    scale_y_continuous(breaks=seq(50, 100, 5)) 

ggsave("iaccptperc.png", width=12, height=9)

# ggplot(initialbyyear, aes(x=Fiscal.Year, y=idenperc)) + 
#     geom_line(aes(color=naics, group=naics), size = 1) + 
#     ggtitle("Line Plot of Industry and  Initial Denials Percentage by Year")+
#     geom_point(aes(color=naics), size=3) +
#     theme(plot.title = element_text(hjust = 0.5)) + 
#     xlab("Year")+ ylab("Percentage(%)")+
#     geom_dl(aes(label = naics, color = naics), method = list(dl.combine("first.polygons", "last.polygons"), cex = 1))+
#     scale_x_continuous(breaks=seq(2009, 2019, 1))+
#     scale_y_continuous(breaks=seq(50, 100, 5))
# ggsave("idenperc.png", width=12, height=9)


```
54(	Professional, Scientific, and Technical Services) changed significant between 2009 to 2010.
54 is also changed significant between 2017 to 2018 which is 29.37%. The second one is 11(Agriculture, Forestry, Fishing and Hunting) 28.51.
49(Transportation and Warehousing) changed significant between 2014-2015.
51 (Information) changed the least betwen 2017 to 2018 which is 1.78, the second one is 42(Wholesale Trade) 1.79.


### 3.3.2: Continuing Application

```{r fig.width=12, fig.height=9, continuewithyear, echo = 0}
#use group by to combine same industry together to calculate the total continuing application amount.
continuingbyyear <- h1b %>% group_by(Fiscal.Year, naics) %>% summarize(totalconaccpt = sum(Continuing.Approvals, na.rm = T),
                                                  totalconden = sum(Continuing.Denials, na.rm = T),
                                                  totalcontinue = sum(Continuing.Approvals,na.rm = T)+sum(Continuing.Denials,na.rm = T),
                                                  caccptperc = (totalconaccpt/totalcontinue) * 100,
                                                  cdenperc = ( totalconden /totalcontinue) * 100 )

head(continuingbyyear,n=5)
ggplot(continuingbyyear, aes(x=Fiscal.Year, y=caccptperc)) + 
    geom_line(aes(color=naics, group=naics), size = 1) + 
    ggtitle("Line Plot of Industry and Continuing Approvals Percentage by Year")+
    geom_point(aes(color=naics), size=3) +
    theme(plot.title = element_text(hjust = 0.5)) + 
    xlab("Year")+ ylab("Percentage(%)")+
    geom_dl(aes(label = naics, color = naics), method = list(dl.combine("first.polygons", "last.polygons"), cex = 1))+
    scale_x_continuous(breaks=seq(2009, 2019, 1))+
    scale_y_continuous(breaks=seq(50, 100, 5))

ggsave("caccptperc.png", width=12, height=9)

# ggplot(continuingbyyear, aes(x=Fiscal.Year, y=cdenperc)) + 
#     geom_line(aes(color=naics, group=naics),size = 1) + 
#     ggtitle("Line Plot of Industry and Continuing Denials Percentage by Year")+
#     geom_point(aes(color=naics), size=3) +
#     theme(plot.title = element_text(hjust = 0.5)) + 
#     xlab("Year")+ ylab("Percentage(%)")+
#     geom_dl(aes(label = naics, color = naics), method = list(dl.combine("first.polygons", "last.polygons"), cex = 1))+
#     scale_x_continuous(breaks=seq(2009, 2019, 1))+
#     scale_y_continuous(breaks=seq(50, 100, 5))
# 
# ggsave("cdenperc.png", width=12, height=9)

```
11(Agriculture, Forestry, Fishing and Hunting) changed the most in 2018 which is 20.43, the second one is 54 (Professional, Scientific, and Technical Services).
in 2018, 61(Educational Services) changed the least which is 0.1, the second one is 82(Other Services (except Public Administration)) 0.26.








# Citation

What is H1B Visa? (n.d.). Retrieved October 14, 2019, from https://www.path2usa.com/what-is-h1b-visa.

USCIS Reaches FY 2019 H-1B Cap. (2018, April 6). Retrieved October 14, 2019, from https://www.uscis.gov/news/alerts/uscis-reaches-fy-2019-h-1b-cap.

Buy American and Hire American. (2019, April 26). Retrieved October 14, 2019, from https://www.uscis.gov/legal-resources/buy-american-hire-american-putting-american-workers-first.

Kumar. (2019, May 26). H1B Historical Data – Lottery vs 85K Quota, Masters vs Regular Split. Retrieved October 22, 2019, from https://redbus2us.com/h1b-historical-data-lottery-vs-85k-quota-masters-vs-regular-split/.

Search NAICS Codes by Industry. (n.d.). Retrieved October 15, 2019, from https://www.naics.com/search-naics-codes-by-industry/.

SIC Major Group: 99 Nonclassifiable Establishments. (n.d.). Retrieved October 21, 2019, from https://www.naics.com/standard-industrial-code-divisions/?code=99.

Zaveri, P., & Roy, A. (2019, April 2). Changes to H-1B visa lottery create 'stress' for tech companies and employees. Retrieved October 22, 2019, from https://www.cnbc.com/2019/04/01/h1-b-lottery-changes-in-2018-masters-candidates-more-inspections.html.
