---
title: "H-1B Visa"
author: "Spencer Stucky, Cheng Zeng, Wenyu Zeng, Chao Zhou"
date: "10/14/2019"
output:
  html_document:
    toc: yes
    toc_depth: 4
    fig.align: "center"
    toc_float: yes
    theme: readable
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r, include = F}
library(dplyr)
library(maps)
h1b <- read.csv('h1b_datahubexport_2009-2019.csv')
#h1b <- h1b[h1b$State %in%state.abb,]
```
How have U.S. H1b visa acceptances and denials changed over the course of 2015-2019?1a) How does industry effect H1b visas from the time spanning 2015-2019?

# Chapter 1: Introduction

H-1B visa is a type of non-immigrate visa of United States that under the Immigration and Nationality Act since 1952. This visa allows foreign workers (individual) to enter United Stated to temporarily be employed by U.S. employers in specialty occupations. (Path2usa) With the development of the world, more and more people are looking for opportunities in U.S. Therefore, the number of applications for H-1B are rising every year. Each year, the total number of H-1B petitions that U.S. congress allowed to approve for a fiscal year is 65,000 for regular cap and 20,000 master’s exemption. (USCIS) According to the summary of USCIS H-1B 2019, there are more than 190,000 applications were submitted and 94,213 for regular quota and 95,885 for master quota. (USCIS) However, after Donald Trump become president, he signed the "Buy American, Hire American" executive order in April 2017. (USCIS) Though, this order helps U.S. employers hire most-skills foreign employees, the approval of this visa became harder and harder.

Nonetheless, politics is not the only factor that affects H-1B’s approval rate, but industries and location are also impact it. In this report, we will focus on the relationship in _______fill in the blank_______________________________________.

# Chapter 2: Description of Data

The source data 
```{r, echo=FALSE}
str(h1b)
```
xxxxxxx

# Chapter 3: Location Factor

## 3.1: Industries vs NAICS 

In this Chapter, we are 

### 3.1.1: S.M.A.R.T Question


Meow Meow Meow 








# Chapter 4: Industries Factor

## 4.1: Industries vs NAICS 

In this Chapter, we are 

### 4.1.1: S.M.A.R.T Question

**Does industry relates to the H-1B initial or continuing approval and denial rate between 2009-2019?**

### 4.2.1: Initial Application

```{r initial, echo=FALSE} 
library(ggplot2)
h1b$naics = as.factor(h1b$NAICS)
# use group by to combine same industry together to calculate the total initial application amount.
initial <- h1b %>% group_by(naics) %>% summarize( totaliniaccpt = sum(Initial.Approvals, na.rm = T), #shows total number of initail approvals
                                                  totaliniden = sum(Initial.Denials, na.rm = T), # shows total number of initial denials
                                                  totalinitial = sum(Initial.Approvals,na.rm = T)+sum(Initial.Denials,na.rm = T), # shows total number of initial application
                                                  iaccptperc = (totaliniaccpt/totalinitial)*100, # percentage of initial approval rate
                                                  idenperc = (totaliniden/totalinitial)*100) #percentage of initial denial rate
# 
# ggplot(initial, aes(x = naics, y = iaccptperc, color = naics, fill = naics)) + # percentage of initial approvals rate and color by industry code
#   geom_bar(stat ="identity") +
#   xlab("NAICS CODE") +
#   ylab("Total Initial Approvals Percentage")
# 
# ggsave("Total Initial Approvals Percentage.png", width=12, height=9)

ggplot(initial, aes(x = naics, y = idenperc, color = naics, , fill = naics)) + # percentage of initial denials rate and color by industry code
  geom_bar(stat ="identity") + 
  xlab("NAICS CODE") + 
  ylab("Total Initial Denials Percentage") 

#ggsave("Total Denial Approvals Percentage.png", width=12, height=9)


```

21(Mining): highest approval rate and lowest denial rate. 
https://www.thermofisher.com/blog/mining/mining-industry-employees-are-in-demand/
https://www.smenet.org/SME/media/Government/201201_EmergingWorkforceTrendsinUSMiningIndustry.pdf

There is a fair amount of information available on degreed mining-related programs in the U.S. and globally. The information on community colleges, trade schools, apprentice programs and other mining training and education programs is spotty at best. Information on unskilled labor at mines was also lacking though, from conversations with recruiters and personal experience, there are few if any mining jobs that do not require training. What follows focuses on the degreed programs in mining. Will there be enough degreed and skilled labor to meet the current and anticipated demand? The answer to this question is unclear because current demand is not known. Discussions with recruiters that specialize in the mining industry indicate that, generally speaking, there is currently not enough skilled labor to meet the demand although demand varies depending on location and position. There are however, numerous current news articles (U.S. and foreign) that suggest there is a mine labor shortage.

Within this world framework, U.S. mining finds itself with a predominantly senior workforce and an expanding need for labor to meet the increasing resource demand. As a result, the U.S. may, in the short term, be challenged to process its mineral resources and would therefore be strategically exposed due to its dependence on foreign raw materials. 

72(Accommodation and Food Services): lowest approval rate and highest denial rate

need a lot of worker but most of accommodation and food services is small business. which doesn't fullfill the requirment of H1B. Also, especially for hospitality industry, has seasonal impact. they are more looking for H2B (Temporary Non-agricultural Worker). Therefore, the denial rate is really high.

https://www.h1b.biz/hospitality-and-immigration-law-visas-for-chefs-cooks-and-other.html

https://www.chicagotribune.com/business/ct-hospitality-needs-more-immigrants-report-0825-biz-20170824-story.html

### 4.2.2: Continuing Application
```{r continuing, echo=FALSE}
# use group by to combine same industry together to calculate the total continuing application amount.
continuing <- h1b %>% group_by(naics) %>% summarize( totalconaccpt = sum(Continuing.Approvals, na.rm = T),
                                                  totalconden = sum(Continuing.Denials, na.rm = T),
                                                  totalcontinue = sum(Continuing.Approvals,na.rm = T)+sum(Continuing.Denials,na.rm = T),
                                                  caccptperc = (totalconaccpt/totalcontinue) * 100,
                                                  cdenperc = ( totalconden /totalcontinue) * 100 )
# ggplot(continuing, aes(x = naics, y = caccptperc, color = naics, fill = naics)) + geom_bar(stat ="identity") + xlab("NAICS CODE") + ylab("Total Continuing Approvals Percentage")
# ggsave("Total Continuing Approvals Percentage.png", width=12, height=9)

ggplot(continuing, aes(x = naics, y = cdenperc, color = naics, fill = naics)) + geom_bar(stat ="identity") + xlab("NAICS CODE") + ylab("Total Continuing Denials Percentage")

#ggsave("Total Continuing DenialsPercentage.png", width=12, height=9)
```
99: This major group includes establishments which cannot be classified in any other industry. Establishments which can be classified in a division should be classified in the most appropriate industry within that division.
99(Nonclassifiable Establishments): lowest appoval rate and highest denial rate
55(Management of Companies and Enterprises): highest approval rate and lowest denial rate. Financial & Banking.

Some bank departments are now focusing their hiring on workers who don’t need permits, though they continue to use the visas for positions such as engineers and quantitative analysts that are hard to fill with US workers.

Eight major investment banks increased their H-1B applications for high-skilled workers by almost 60% over five years to more than 7,000 in fiscal year 2017, according to a Bloomberg analysis of visa filing data.

The banks, including JPMorgan Chase & Co. and Goldman Sachs Group Inc., increasingly have been using a similar approach to hiring as tech companies, which rely most heavily on the visas. To hire foreign workers under the program, companies compete in a government lottery for a share of the 85,000 permits available annually.

## 4.3: Industries vs NAICS by Year

### 4.3.1: Initial Application

```{r fig.width=12, fig.height=9,initialwithyear, echo=F}
#install.packages("directlabels")
library(directlabels)

initialbyyear <- h1b %>% group_by(Fiscal.Year, naics) %>% summarize( totaliniaccpt = sum(Initial.Approvals, na.rm = T),
                                                  totaliniden = sum(Initial.Denials, na.rm = T),
                                                  totalinitial = sum(Initial.Approvals,na.rm = T)+sum(Initial.Denials,na.rm = T),
                                                  iaccptperc = (totaliniaccpt/totalinitial)*100, 
                                                  idenperc = (totaliniden/totalinitial)*100)


ggplot(initialbyyear, aes(x=Fiscal.Year, y=iaccptperc)) + 
    geom_line(aes(color=naics, group=naics), size = 1) +   # create the line by nacis code
    ggtitle("Line Plot of Industry and  Initial Approvals Percentage by Year")+
    geom_point(aes(color=naics), size=3) +  # for visualization purpose, we set up the point for each year so people can directly see the rate change of industry by year 
    theme(plot.title = element_text(hjust = 0.5)) +  # since we change the size of the figer, we need to relocate the fig name to center
    xlab("Year")+ ylab("Percentage(%)")+  # rename x and y axis names
    geom_dl(aes(label = naics, color = naics), method = list(dl.combine("first.polygons", "last.polygons"), cex = 1))+  #set up label for each line
    scale_x_continuous(breaks=seq(2009, 2019, 1))+   # changing the scale for both x and y axis
    scale_y_continuous(breaks=seq(50, 100, 5)) 

#ggsave("iaccptperc.png", width=12, height=9)

#write.csv(initialbyyear, file = "initialbyyear.csv")

# ggplot(initialbyyear, aes(x=Fiscal.Year, y=idenperc)) + 
#     geom_line(aes(color=naics, group=naics), size = 1) + 
#     ggtitle("Line Plot of Industry and  Initial Denials Percentage by Year")+
#     geom_point(aes(color=naics), size=3) +
#     theme(plot.title = element_text(hjust = 0.5)) + 
#     xlab("Year")+ ylab("Percentage(%)")+
#     geom_dl(aes(label = naics, color = naics), method = list(dl.combine("first.polygons", "last.polygons"), cex = 1))+
#     scale_x_continuous(breaks=seq(2009, 2019, 1))+
#     scale_y_continuous(breaks=seq(50, 100, 5))
# ggsave("idenperc.png", width=12, height=9)


```
54(	Professional, Scientific, and Technical Services) changed significant between 2009 to 2010 15.68. 
https://fas.org/sgp/crs/misc/97-746.pdf
https://www.bls.gov/opub/btn/volume-2/careers-in-growing-field-of-information-technology-services.htm

54 is also changed significant between 2017 to 2018 which is 29.37%. 

Since 2003, employment in the IT industry has grown by 37 percent. During the recent recession (December 2007 to June 2009), the industry lost only 1 percent of its workforce in 2009, but otherwise maintained employment. By 2010, employment had recovered and was higher than it had been in 2008.

https://www.vox.com/2019/2/28/18241522/trump-h1b-tech-work-jobs-overseas
https://insights.dice.com/2018/09/18/new-h-1b-rule-bad-large-tech-companies/




### 4.3.2: Continuing Application

```{r fig.width=12, fig.height=9, continuewithyear, echo = 0}
#use group by to combine same industry together to calculate the total continuing application amount.
continuingbyyear <- h1b %>% group_by(Fiscal.Year, naics) %>% summarize(totalconaccpt = sum(Continuing.Approvals, na.rm = T),
                                                  totalconden = sum(Continuing.Denials, na.rm = T),
                                                  totalcontinue = sum(Continuing.Approvals,na.rm = T)+sum(Continuing.Denials,na.rm = T),
                                                  caccptperc = (totalconaccpt/totalcontinue) * 100,
                                                  cdenperc = ( totalconden /totalcontinue) * 100 )


ggplot(continuingbyyear, aes(x=Fiscal.Year, y=caccptperc)) + 
    geom_line(aes(color=naics, group=naics), size = 1) + 
    ggtitle("Line Plot of Industry and Continuing Approvals Percentage by Year")+
    geom_point(aes(color=naics), size=3) +
    theme(plot.title = element_text(hjust = 0.5)) + 
    xlab("Year")+ ylab("Percentage(%)")+
    geom_dl(aes(label = naics, color = naics), method = list(dl.combine("first.polygons", "last.polygons"), cex = 1))+
    scale_x_continuous(breaks=seq(2009, 2019, 1))+
    scale_y_continuous(breaks=seq(50, 100, 5))

#ggsave("caccptperc.png", width=12, height=9)

# ggplot(continuingbyyear, aes(x=Fiscal.Year, y=cdenperc)) + 
#     geom_line(aes(color=naics, group=naics),size = 1) + 
#     ggtitle("Line Plot of Industry and Continuing Denials Percentage by Year")+
#     geom_point(aes(color=naics), size=3) +
#     theme(plot.title = element_text(hjust = 0.5)) + 
#     xlab("Year")+ ylab("Percentage(%)")+
#     geom_dl(aes(label = naics, color = naics), method = list(dl.combine("first.polygons", "last.polygons"), cex = 1))+
#     scale_x_continuous(breaks=seq(2009, 2019, 1))+
#     scale_y_continuous(breaks=seq(50, 100, 5))
# 
# ggsave("cdenperc.png", width=12, height=9)

```
11(Agriculture, Forestry, Fishing and Hunting) changed the most in 2018 which is 20.43, the second one is 54 (Professional, Scientific, and Technical Services).

https://www.cfr.org/backgrounder/us-temporary-foreign-worker-programs
https://www.cato.org/blog/immigration-application-denials-jump-37-percent-under-trump








# Chapter 5: Year (& Policy) Factor

## 5.1: Industries vs NAICS 

In this Chapter, we are 

### 5.1.1: S.M.A.R.T Question

Donald Trump?!!!!!!!!!





# Chapter 6: Conculsion 


no idea~~~~~~




# Citation

What is H1B Visa? (n.d.). Retrieved October 14, 2019, from https://www.path2usa.com/what-is-h1b-visa.

USCIS Reaches FY 2019 H-1B Cap. (2018, April 6). Retrieved October 14, 2019, from https://www.uscis.gov/news/alerts/uscis-reaches-fy-2019-h-1b-cap.

Buy American and Hire American. (2019, April 26). Retrieved October 14, 2019, from https://www.uscis.gov/legal-resources/buy-american-hire-american-putting-american-workers-first.

Kumar. (2019, May 26). H1B Historical Data – Lottery vs 85K Quota, Masters vs Regular Split. Retrieved October 22, 2019, from https://redbus2us.com/h1b-historical-data-lottery-vs-85k-quota-masters-vs-regular-split/.

Search NAICS Codes by Industry. (n.d.). Retrieved October 15, 2019, from https://www.naics.com/search-naics-codes-by-industry/.

SIC Major Group: 99 Nonclassifiable Establishments. (n.d.). Retrieved October 21, 2019, from https://www.naics.com/standard-industrial-code-divisions/?code=99.

Zaveri, P., & Roy, A. (2019, April 2). Changes to H-1B visa lottery create 'stress' for tech companies and employees. Retrieved October 22, 2019, from https://www.cnbc.com/2019/04/01/h1-b-lottery-changes-in-2018-masters-candidates-more-inspections.html.

Yang, Y. (2018, February 22). Big Banks in U.S. Forced to Reevaluate Hiring Foreign Workers. Retrieved October 23, 2019, from https://www.bloomberg.com/news/articles/2018-02-22/big-banks-in-u-s-forced-to-reevaluate-hiring-foreign-workers.